BIOL 274 Homework 4

### 2024-02-10 bio_dynamics/bio274_hw4.Rmd
bio hw 4 prob 2

---
title: "BIOL 274 Homework 4"
author: "Ruby Krasnow"
date: "2024-02-09"
output:
  pdf_document:
    extra_dependencies: ["derivative", "tcolorbox", "xcolor"]
---

@@

$\lambda^2+\frac{k}{m}=0$

@@

@@

@@

$y(t)=\cos{(\sqrt{\frac{k}{m}} t)}$
$y'(t)=-\sqrt{\frac{k}{m}}\sin{(\sqrt{\frac{k}{m}} t)}$
$y''(t)=-\frac{k}{m}\cos{(\sqrt{\frac{k}{m}} t)}$

Then $y''+\frac{k}{m}y=-\frac{k}{m}\cos{(\sqrt{\frac{k}{m}} t)}+\frac{k}{m}\cos{(\sqrt{\frac{k}{m}} t)}=0$

@@

$A= \frac{4B}{7}$
$$-\frac{16B}{7}-\frac{49B}{7}=1 $$
Which gives us that $B=\frac{-7}{65}, \; A= \frac{-4}{65}$.
Thus, our particular solution is 
$$y_p=-\frac{4}{65} \sin{(2t)}-\frac{7}{65}\cos{(2t)}$$

>>>>

---
title: "BIOL 274 Homework 4"
author: "Ruby Krasnow"
date: "2024-02-10"
output:
  pdf_document:
    extra_dependencies: ["derivative", "tcolorbox", "xcolor"]
---

@@

$$\lambda^2+\frac{k}{m}=0$$

@@

We can check this:
$$y(t)=\cos{(\sqrt{\frac{k}{m}} t)}$$
$$y'(t)=-\sqrt{\frac{k}{m}}\sin{(\sqrt{\frac{k}{m}} t)}$$
$$y''(t)=-\frac{k}{m}\cos{(\sqrt{\frac{k}{m}} t)}$$
$$y''+\frac{k}{m}y=-\frac{k}{m}\cos{(\sqrt{\frac{k}{m}} t)}+\frac{k}{m}\cos{(\sqrt{\frac{k}{m}} t)}=0$$

@@

$y(0)=\cos{(0)}=1$, so we must have the initial condition $y(0)=1$.

@@

In the equation for simple harmonic oscillation $y(t) = A \cos(\omega t + \varphi)$, $\omega=\sqrt{\frac{k}{m}}$ represents the angular frequency, measured in radians per second. $\omega$ is equivalent to $\frac{2\pi}{T}$, where $T$ is the period of the oscillation (the time it takes to complete one oscillation and return to the starting position). This means we can find T by taking $\frac{2\pi}{\omega}=\frac{2\pi}{\sqrt{\frac{k}{m}}}$, or
$$T=2\pi \sqrt{\frac{m}{k}}$$

@@

$$A= \frac{4B}{7}$$
$$-\frac{16B}{7}-\frac{49B}{7}=1 $$
Which gives us that $B=\frac{-7}{65}, \; A= \frac{-4}{65}$.
Thus, our particular solution is 
$$y_p=-\frac{4}{65} \sin{(2t)}-\frac{7}{65}\cos{(2t)}$$
